---
title: "Analysis Export"
author: "William H. Rogers"
date: "April 9, 2015"
output: html_document
---

# Objective
  *  Create tables to match Anne's paper for all years of the CPS.
  *  Document the expected working life
  *  Estimate the age profile using three quadratic equations:
    + With education shifter
    + With education and marrital status shifter
    + With all shifters and marrital-age interaction 
  * Similate age profile across age range
  * Collect regression summary stats

# Import Data and Packages

```{r packages}
library(survey)
library(parallel)
library(texreg)
```


```{r import}
load("data/main-data-cps-all-years.RData")
```

# Expected Age

```{r expected-age-1}
sim_ages <- 25:75
sim_edu <- levels(cps_svy[[1]]$variables$edu_rcd)
sim_hh <- levels(cps_svy[[1]]$variables$hh_rcd)
len_ages <- length(25:75)
len_edu <- length(sim_edu)
len_hh <- length(sim_hh)
```

```{r expected-age-2}
sim_vars_a <- data.frame(
  a_age = sim_ages, 
  edu_rcd = rep(sim_edu, each = len_ages)
  )

sim_vars_b <- data.frame(
  a_age = sim_ages, 
  edu_rcd = rep(sim_edu, each = len_ages), 
  hh_rcd = rep(sim_hh, each = len_ages*len_edu)
  )
```

# Desciptive Tables

```{r desc-tabs}
cl <- makeCluster(7)
clusterEvalQ(cl, library(survey))
clusterEvalQ(cl, library(texreg))

tbl_age_group <- parLapply(
  cl, cps_svy, 
  function(x){
    survey::svyby(
      ~ pearnval, 
      ~ age_rcd + edu_rcd + hh_rcd, 
      x, svymean, 
      keep.names = FALSE
     ) 
   }
  )

stopCluster(cl)

tbl_age_group <- lapply(
  names(tbl_age_group), 
  function(x){transform(tbl_age_group[[x]], year = as.numeric(x))}
  )

tbl_age_group <- do.call("rbind", tbl_age_group)
```

# Age Profile

```{r mld-fun}
mdl_fun_a <- pearnval ~ edu_rcd + a_age + I(a_age ^ 2)
mdl_fun_b <- pearnval ~ edu_rcd + hh_rcd + a_age + I(a_age ^ 2)
mdl_fun_c <- pearnval ~ edu_rcd + hh_rcd*a_age + hh_rcd*I(a_age ^ 2)
```

```{r ols}
mdl_ols_a <- lapply(
  cps_svy, 
  function(x){
    lm_out <- lm(mdl_fun_a, data = x$variables)
    list(
      tab = extract(lm_out), 
      sim = cbind(sim_vars_a, predict(lm_out, sim_vars_a))
    )}
  )

mdl_ols_b <- lapply(
  cps_svy, 
  function(x){
    lm_out <- lm(mdl_fun_b, data = x$variables)
    list(
      tab = extract(lm_out), 
      sim = cbind(sim_vars_b, predict(lm_out, sim_vars_b))
    )}
  )

mdl_ols_c <- lapply(
  cps_svy, 
  function(x){
    lm_out <- lm(mdl_fun_c, data = x$variables)
    list(
      tab = extract(lm_out), 
      sim = cbind(sim_vars_b, predict(lm_out, sim_vars_b))
    )}
  )
```

```{r ols-sim}
mdl_ols_c_sim <- lapply(
  names(mdl_ols_c), 
  function(x){
    transform(mdl_ols_c[[x]][[2]], year = as.numeric(x))
  }
  )
mdl_ols_c_sim <- do.call("rbind", mdl_ols_c_sim)
```

# Save Results

```{r save}
save(
  tbl_age_group,
  file = "data/analysis-export.RData"
  )
```

